Asymmetric relationships and their effects on coexistence

### 2023-02-24 paper/Paper.Rnw
problems with the R chunk in paper.Rnw identified and commented

#place R code here for loading in necessary variables from Results
#ordinarily this would be a readRDS command, but I'm just defining a variable here for now
#allregres<-matrix(rnorm(10),2,5)
res_loc <- "../results_numeric/"
fig2 <- readRDS(file="../results_numeric/fig2data.RDS")
M <- readRDS(file="../results_numeric/M.RDS")
se3 <- readRDS(file="../results_numeric/fig3maxse.RDS")
se4 <- readRDS(file="../results_numeric/fig4maxse.RDS")
se5 <- readRDS(file=paste0(res_loc, "fig5maxse.RDS"))
se6 <- readRDS(file=paste0(res_loc, "fig6maxse.RDS"))
@

>>>>

#place R code here for loading in necessary variables from Results
res_loc <- "../results_numeric/"
#fig2 <- readRDS(file=paste0(res_loc,"fig2data.RDS"))
M <- readRDS(file=paste0(res_loc,"M.RDS"))
se3 <- readRDS(file=paste0(res_loc,"fig3maxse.RDS"))
#se4 <- readRDS(file=paste0(res_loc,"fig4maxse.RDS"))
se4<-NA
se5 <- readRDS(file=paste0(res_loc, "fig5maxse.RDS"))
se6 <- readRDS(file=paste0(res_loc, "fig6maxse.RDS"))
@
